---
title: "Data Translation Write Up"
author: "Rosalie Sherry"
date: "2/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Assignment
You don’t have to write a lot here. Just make an RMarkdown file that performs your analysis and displays the results, and in which you explain your analysis.

Be sure to:

Include at least one regression and one graph
Explain why you are performing the analysis you are performing, and the choices you made in putting it together
Explain how your analysis addresses the research question
Any additional analyses you did that led you to design your main analysis that way (i.e. “I graphed Y vs. X and it looked nonlinear so I added a polynomial term” - you could even include this additional analysis if you like)
Explain what we should conclude, in real world terms, based on your results
There’s no minimum or maximum length. I expect most analyses will be somewhere around two pages of text

library(jtools)
library(tidyverse)
library(png)

## Including Plots

When you go through my code (or perhaps my repository) you will see that my code goes through a lot of changes and adjustment. I first had to tidy the data which was the most time consuming portion of this project. After it took me a long time to figure out how to play with the data, I knew that I was regressing earnings and my index variable. 

First, I choose what was "high" earning and "low" earning based on what the median income was of the median income group. That number is 41,800. Which I save as "median_earnings" and also shoutout in the code. So if it was greater than or equal to 41,800 it was grouped as "high" and everything else was "low". 
Next, standardizing the Index number was done by using the demeaning approach we learned last week. Index - mean(index). This was to bring everything in close together so the data was easier to work with.

Now that I had gotten to being able to work with the data it was time to get down to the nitty gritty and actually start interpreting it. I had a variety of issues with this, I could not decide whether to control for University type or whether to filter by university type. So I ran regressions based on both. I did not want to ignore university type because I have my own bias that I assume others have as well. And by this I mean, I chose to go to Gonzaga over the University of Washington for undergrad for a variety of reasons but one major factor is that I assumed (and was told by those giving me advice) that private schools have better alumni networks and with that goes better job opportunities. So in part, I wanted to test whether or not this was true but I also wanted to make sure I was looking at each entity as individuals in case there was any externalities such as what I had listed that might throw my testing. 

I then ran approximately 8,000,000 regressions and did a lot of different graphing to see what worked, what didn't, and what I should pay attention to. Should Control be filtered to University type or should I use it as a factor? What do all these regressions show me? Approximately none of them were linear when I ran them and so I played around with the equation.

```{r pressure, echo=TRUE}

source("Code/Sherry_Data_Exploration_Assignment.R")
ggplot(data = HighEarnAfterSept, aes(sd_index)) +
  geom_histogram(fill = 'pink') +
  facet_grid(CONTROL ~ .) + ggtitle('High Earn After September')


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}

```

